Network Attributes by Walkshed

### 2023-06-16 data-raw/01-OSM-Network-and-Routing.Rmd
Recreated routing and walksheds after cleaning the zoning system and adding validation points

Load packages:
```{r}
# Allocate memory for routing
options(java.parameters = "-Xmx20G")

@@

@@

Notice that some DAs appear twice after intersecting with urban fabric types:
```{r}
urban_hammer_da |> 
  left_join(
    urban_hammer_da |> 
      st_drop_geometry() |>
      group_by(GeoUID) |>
      summarize(n = n()),
    by = "GeoUID") |>
  ggplot() +
  geom_sf(aes(fill = factor(n)))

```

This is not a problem. In most cases, some DAs will get two walksheds instead of one.

Coordinates of centroids of the DAs that intersect urban/suburban types (in lat-long). These will be the origins of trips, that is, our proxies for "neighborhoods":
```{r}
origins <- st_centroid(urban_hammer_da) |>
  st_transform(crs = st_crs(4326))
```

@@

```{r}
destinations_h3 <- h3_to_geo(urban_hammer_h3)
```

@@

Prepare Input Data for `r5r`. The origins are the coordinates of the DAs and the destinations the coordinates of the h3 geohashes:
```{r prepare-inputs}
# save origins in format expected by R5R (id, lon, lat)
origins_i <- data.frame(ID = origins$GeoUID, 
                        origins |>
                          st_transform(crs = 4326) |>
                          st_coordinates()) |>
  rename(lon = X, lat = Y, id = ID) |>
  dplyr::select(id, lon, lat)

# now vaccination sites
destinations_j <- data.frame(id = urban_hammer_h3, 
                             lat = destinations_h3[,1],
                             lon = destinations_h3[,2])
```

Calculate OD Matrix for walking:
```{r calculate walk od matrix}

# set up batching according to how many origin rows to process at one time
chunksize = 4000 # larger chunks for walking will give enough origins in each chunk to allow multiprocessing to spin up with R5R
num_chunks = ceiling(nrow(origins_i)/chunksize)

# create origin-destination pairs
origins_chunks <- as.disk.frame(origins_i,
                                outdir = "./df/origins_i",
                                nchunks = num_chunks,
                                overwrite = TRUE)

@@

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "./df/output_ttm_walk",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}

@@

## Extract travel time matrix

```{r load od matrix for walk, include=FALSE}
# connect to the walking travel time matrix disk frame
ttm_walk.disk.frame <- disk.frame("./df/output_ttm_walk")
#opportunities_j <- as.data.frame(nyc_cb_point) |> select(GEOID10, total_emp) |> rename(toId = GEOID10, o_j = total_emp)
```

Convert disk.frame to data frame:
```{r}
ttm_walk <- as.data.frame(ttm_walk.disk.frame) |>
  transmute(GeoUID = from_id, h3_index = to_id, travel_time = travel_time_p50)
```

@@

Retrieve the h3 areas as multipolygons:
```{r}
walksheds <- ttm_walk |> 
  group_by(GeoUID) |>
  group_map(~ h3_set_to_multi_polygon(.x$h3_index),
            .keep = TRUE)
```

Obtain the GeoUIDs of the walksheds:
```{r}
walkshed_GeoUIDs <- ttm_walk |>
  group_by(GeoUID) |>
  summarize(GeoUID = first(GeoUID),
            .groups = "drop")
```

Convert walksheds with GeoUIDs of DAs to a data frame:
```{r}
walksheds <- data.frame(GeoUID = walkshed_GeoUIDs,
                         geometry = purrr::map_df(walksheds,
                            tibble::as_tibble)) |>
  st_as_sf(crs = 4326)

```

Verify the catchments:
```{r}
test_unit = sample.int(nrow(walksheds), 1)

ggplot() +
  geom_sf(data = data_da_2016 |>
            filter(GeoUID == walksheds$GeoUID[test_unit]),
          color = "black",
          fill= NA) + 
  geom_sf(data = walksheds[test_unit,],
          color = "blue",
          fill = NA,
          linewidth = 1)
```

Join the urban type to DAs in the walksheds object:
```{r}
walksheds <- walksheds |>
  left_join(origins |>
              st_drop_geometry() |>
              transmute(GeoUID, Type = Type.1),
            by = "GeoUID")
```

Convert to factor:
```{r}
walksheds <- walksheds |>
  mutate(Type = factor(Type))
```

Summarize the walksheds:
```{r}
summary(walksheds)
```

The DAs and the catchments match. Now save the data objects:
```{r}
save(urban_hammer_da, file = "urban_hammer_da.rda", compress = "xz")
save(ttm_walk, file = "ttm_walk.rda", compress = "xz")
save(walksheds, file = "walksheds.rda", compress = "xz")
```

Calculate area of walksheds:
```{r}
walksheds <- walksheds |>
  mutate(area = st_area(geometry))
```

Summarize by urban type:
```{r}
walksheds |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(area)) |>
  group_by(Type) |>
  skim()
```

```{r}
walksheds |>
  st_drop_geometry() |>
  mutate(area = log(units::drop_units(set_units(area, km2)))) |>
  lm(area ~ Type, data = _) |>
  summary()
```

```{r}
ggplot(data = walksheds |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(set_units(area, km2))),
  aes(x = Type, y = area)) +
  geom_violin()
```

Urban walksheds close to the mean:
```{r}
walksheds |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(area)) |>
  filter(Type == "Urban", area >= 1372092 * 0.999 & area <= 1372092 * 1.001)
```

Suburban walksheds close to the mean area of suburban walksheds:
```{r}
walksheds |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(area)) |>
  filter(Type == "Suburban", area >= 1100484 * 0.99 & area <= 1100484 * 1.01)
```

Compare the areas of walksheds using comparable areas:
```{r}
mock_areas <- data.frame(Type = c("Suburban",
                          "Urban"), 
                 area = c(1100484,
                          1372092),
                 x0 = c(0,0),
                 y0 = c(0,0)) |>
  mutate(r = sqrt(area/pi))
```

```{r}
ggplot() +
  geom_circle(data = mock_areas,
              aes(x0 = x0,
                  y0 = y0,
                  r = r,
                  color = Type))+
  coord_equal()
```

>>>>

Load packages:
```{r warning=FALSE, message=FALSE}
# Allocate memory for routing
options(java.parameters = "-Xmx20G")

@@

Search for duplicates after the intersection:
```{r}
duplicate_DAs <- urban_hammer_da |> 
  st_drop_geometry() |>
  group_by(GeoUID) |> 
  summarize(n = n()) |>
  filter(n > 1)
```

Duplicates are caused by small inconsistencies between the DA boundaries and the urban/suburban boundaries, and the partitions result in slivers of DA:
```{r}
urban_hammer_da |>
  filter(GeoUID %in% duplicate_DAs$GeoUID[sample.int(50, 1)]) |>
  ggplot() +
  geom_sf(aes(fill = GeoUID))
```

This leads to some detritus:
```{r}
urban_hammer_da |>
  filter(GeoUID == "35250031") |>
  ggplot() +
  geom_sf(aes(fill = GeoUID)) +
  geom_sf(data = data_da_2016,
          fill = NA)
```

Summary of areas of the areas of DAs after the intersection. `r` is the area of the zone after the intersection divided by the area of the original DA:
```{r}
urban_hammer_da <- urban_hammer_da |>
  mutate(area = st_area(geometry) |> set_units(km^2)) |>
    mutate(r = area/Shape.Area)

urban_hammer_da |>
  filter(GeoUID %in% duplicate_DAs$GeoUID) |>
  select(GeoUID, Shape.Area, Area..sq.km., area, r) |>
  summary()
```

This is the distribution of the areas of all duplicated DAs
```{r}
urban_hammer_da |>
  filter(GeoUID %in% duplicate_DAs$GeoUID) |>
  ggplot(aes(x = r)) +
  geom_histogram()
```

These are them:
```{r}
ggplot() +
  geom_sf(data = urban_hammer_da |>
            filter(GeoUID %in% duplicate_DAs$GeoUID),
          aes(fill = drop_units(r))) +
  geom_sf(data = data_da_2016,
          fill = NA)
```

Split the table into DAs that had no duplicates and DAs that did:
```{r}
urban_hammer_dup <- urban_hammer_da |>
  st_transform(crs = st_crs(data_da_2016)) |>
  filter(GeoUID %in% duplicate_DAs$GeoUID)

urban_hammer_nondup <- urban_hammer_da |>
  st_transform(crs = st_crs(data_da_2016)) |>
  filter(!(GeoUID %in% duplicate_DAs$GeoUID))
```

Choose areas to keep that are not detritus (areas that are more than 50% of the area of the original DA):
```{r}
urban_hammer_dup <- urban_hammer_dup |>
  filter(r > set_units(0.50, km^2))
```

Replace the geometry by its original geometry:
```{r}
urban_hammer_dup <- urban_hammer_dup |>
  st_drop_geometry() |>
  left_join(data_da_2016 |>
              select(GeoUID),
            by = "GeoUID") |>
  select(-c(area, r)) |>st_as_sf()
```

Bind with non-duplicated DAs (who get to keep the geometry they got after intersecting with the urban types):
```{r}
urban_hammer_da <- rbind(urban_hammer_nondup |>
                           select(-c(area, r)),
                         urban_hammer_dup)
```

@@

Coordinates of centroids of the DAs that intersect urban/suburban types (in lat-long). These will be the origins of trips, that is, our proxies for "neighborhoods":
```{r}
origins_da <- st_centroid(urban_hammer_da) |>
  st_transform(crs = st_crs(4326))
```

Also, sample in urban and suburban zones to replicate the number of points for DAs. We will this as a validation dataset.
```{r}
# For reproducibility
seed <- 22331264
set.seed(seed)

origins_validation_suburban <- st_sample(urban_hammer_da |>
            filter(Type.1 == "Suburban"),
          size = rep(1, nrow(urban_hammer_da |>
            filter(Type.1 == "Suburban")))) |>
  st_as_sf() |>
  mutate(Type = "Suburban")

origins_validation_urban <- st_sample(urban_hammer_da |>
            filter(Type.1 == "Urban"),
          size = rep(1, nrow(urban_hammer_da |>
            filter(Type.1 == "Urban")))) |>
  st_as_sf() |>
  mutate(Type = "Urban")
```

Bind and plot:
```{r}
origins_validation <- rbind(origins_validation_suburban,
                          origins_validation_urban) |>
  st_join(data_da_2016 |>
            select(GeoUID)) |>
  mutate(geometry = x)

ggplot() +
  geom_sf(data = urban_types) + 
  geom_sf(data = origins_validation,
          aes(color = Type))
```

@@

Convert to coordinates and store to use as destinations:
```{r}
destinations_h3 <- h3_to_geo(urban_hammer_h3)
```

@@

Prepare Input Data for `r5r` for the DAs.

The origins are the coordinates of the DAs and the destinations the coordinates of the h3 geohashes:
```{r prepare-inputs}
# save origins in format expected by R5R (id, lon, lat)
origins_i_da <- data.frame(ID = origins_da$GeoUID, 
                        origins_da |>
                          st_transform(crs = 4326) |>
                          st_coordinates()) |>
  rename(lon = X, lat = Y, id = ID) |>
  dplyr::select(id, lon, lat)

# save origins in format expected by R5R (id, lon, lat)
origins_i_validation <- data.frame(ID = origins_validation$GeoUID, 
                        origins_validation |>
                          st_transform(crs = 4326) |>
                          st_coordinates()) |>
  rename(lon = X, lat = Y, id = ID) |>
  dplyr::select(id, lon, lat)

# now destinations sites
destinations_j <- data.frame(id = urban_hammer_h3, 
                             lat = destinations_h3[,1],
                             lon = destinations_h3[,2])
```

Calculate OD Matrix for walking (DAs):
```{r calculate walk od matrix DAs}

# set up batching according to how many origin rows to process at one time
chunksize = 4000 # larger chunks for walking will give enough origins in each chunk to allow multiprocessing to spin up with R5R
num_chunks = ceiling(nrow(origins_i_da)/chunksize)

# create origin-destination pairs
origins_chunks <- as.disk.frame(origins_i_da,
                                outdir = "./df/origins_i_da",
                                nchunks = num_chunks,
                                overwrite = TRUE)

@@

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "./df/output_ttm_walk_da",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}

@@

Calculate OD Matrix for walking (validation points):
```{r calculate walk od matrix validation}

# set up batching according to how many origin rows to process at one time
chunksize = 4000 # larger chunks for walking will give enough origins in each chunk to allow multiprocessing to spin up with R5R
num_chunks = ceiling(nrow(origins_i_validation)/chunksize)

# create origin-destination pairs
origins_chunks <- as.disk.frame(origins_i_validation,
                                outdir = "./df/origins_i_validation",
                                nchunks = num_chunks,
                                overwrite = TRUE)

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "./df/output_ttm_walk_validation",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}

## Extract travel time matrices

For DAs:
```{r load od matrix for walk DAs, include=FALSE}
# connect to the walking travel time matrix disk frame
ttm_walk.disk.frame <- disk.frame("./df/output_ttm_walk_da")
#opportunities_j <- as.data.frame(nyc_cb_point) |> select(GEOID10, total_emp) |> rename(toId = GEOID10, o_j = total_emp)
```

Convert disk.frame to data frame:
```{r}
ttm_walk_da <- as.data.frame(ttm_walk.disk.frame) |>
  transmute(GeoUID = from_id, h3_index = to_id, travel_time = travel_time_p50)
```

For validation points:
```{r load od matrix for walk validation points, include=FALSE}
# connect to the walking travel time matrix disk frame
ttm_walk.disk.frame <- disk.frame("./df/output_ttm_walk_validation")
#opportunities_j <- as.data.frame(nyc_cb_point) |> select(GEOID10, total_emp) |> rename(toId = GEOID10, o_j = total_emp)
```

Convert disk.frame to data frame:
```{r}
ttm_walk_validation <- as.data.frame(ttm_walk.disk.frame) |>
  transmute(GeoUID = from_id, h3_index = to_id, travel_time = travel_time_p50)
```

@@

For DAs: retrieve the h3 areas as multipolygons:
```{r}
start.time <- Sys.time()

walksheds_da <- ttm_walk_da |> 
  group_by(GeoUID) |>
  group_map(~ h3_set_to_multi_polygon(.x$h3_index),
            .keep = TRUE)

Obtain the GeoUIDs of the walksheds:
```{r}
walkshed_GeoUIDs_da <- ttm_walk_da |>
  group_by(GeoUID) |>
  summarize(GeoUID = first(GeoUID),
            .groups = "drop")
```

Convert walksheds with GeoUIDs of DAs to a data frame:
```{r}
start.time <- Sys.time()

walksheds_da <- data.frame(GeoUID = walkshed_GeoUIDs_da,
                         geometry = purrr::map_df(walksheds_da,
                            tibble::as_tibble)) |>
  st_as_sf(crs = 4326)

For validation points: retrieve the h3 areas as multipolygons:
```{r}
start.time <- Sys.time()

walksheds_validation <- ttm_walk_validation |> 
  group_by(GeoUID) |>
  group_map(~ h3_set_to_multi_polygon(.x$h3_index),
            .keep = TRUE)

Obtain the GeoUIDs of the walksheds:
```{r}
walkshed_GeoUIDs_validation <- ttm_walk_validation |>
  group_by(GeoUID) |>
  summarize(GeoUID = first(GeoUID),
            .groups = "drop")
```

Convert walksheds with GeoUIDs of DAs to a data frame:
```{r}
start.time <- Sys.time()

walksheds_validation <- data.frame(GeoUID = walkshed_GeoUIDs_validation,
                         geometry = purrr::map_df(walksheds_validation,
                            tibble::as_tibble)) |>
  st_as_sf(crs = 4326)

Verify the catchments:
```{r}
test_unit = sample.int(nrow(walksheds_da), 1)

ggplot() +
  geom_sf(data = data_da_2016 |>
            filter(GeoUID == walksheds_da$GeoUID[test_unit]),
          color = "black",
          fill= NA) + 
  geom_sf(data = walksheds_da[test_unit,],
          color = "blue",
          fill = NA,
          linewidth = 1)
```

```{r}
test_unit = sample.int(nrow(walksheds_validation), 1)

ggplot() +
  geom_sf(data = data_da_2016 |>
            filter(GeoUID == walksheds_validation$GeoUID[test_unit]),
          color = "black",
          fill= NA) + 
  geom_sf(data = walksheds_validation[test_unit,],
          color = "blue",
          fill = NA,
          linewidth = 1)
```

Join the urban type to DAs in the walksheds_da object:
```{r}
walksheds_da <- walksheds_da |>
  left_join(origins_da |>
              st_drop_geometry() |>
              transmute(GeoUID, Type = Type.1),
            by = "GeoUID")
```

Join the urban type to DAs in the walksheds_validation object:
```{r}
walksheds_validation <- walksheds_validation |>
  left_join(origins_validation |>
              st_drop_geometry() |>
              transmute(GeoUID, Type = Type),
            by = "GeoUID")
```

Convert to factor:
```{r}
walksheds_da <- walksheds_da |>
  mutate(Type = factor(Type))

walksheds_validation <- walksheds_validation |>
  mutate(Type = factor(Type))
```

Summarize the walksheds:
```{r}
summary(walksheds_da)

summary(walksheds_validation)
```

The DAs and the catchments match. Now save the data objects:
```{r}
save(urban_hammer_da, file = "urban_hammer_da.rda", compress = "xz")
save(ttm_walk_da, file = "ttm_walk_da.rda", compress = "xz")
save(walksheds_da, file = "walksheds_da.rda", compress = "xz")
save(ttm_walk_validation, file = "ttm_walk_validation.rda", compress = "xz")
save(walksheds_validation, file = "walksheds_validation.rda", compress = "xz")
```

Calculate area of walksheds:
```{r}
walksheds_da <- walksheds_da |>
  mutate(area = st_area(geometry))

walksheds_validation <- walksheds_validation |>
  mutate(area = st_area(geometry))
```

Summarize DA walksheds by urban type:
```{r}
walksheds_da |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(area)) |>
  group_by(Type) |>
  skim()
```

Summarize validation walksheds by urban type:
```{r}
walksheds_validation |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(area)) |>
  group_by(Type) |>
  skim()
```

Linear model of walksheds area as a function of urban type:
```{r}
walksheds_da |>
  st_drop_geometry() |>
  mutate(area = log(units::drop_units(set_units(area, km2)))) |>
  lm(area ~ Type, data = _) |>
  summary()
```

Linear model of walksheds area as a function of urban type:
```{r}
walksheds_validation |>
  st_drop_geometry() |>
  mutate(area = log(units::drop_units(set_units(area, km2)))) |>
  lm(area ~ Type, data = _) |>
  summary()
```

```{r}
ggplot(data = rbind(walksheds_da |>
                      mutate(source = "DAs"),
                    walksheds_validation |>
                      mutate(source = "validation")) |>
  st_drop_geometry() |>
  mutate(area = units::drop_units(set_units(area, km2))),
  aes(x = Type, y = area)) +
  geom_violin() +
  facet_wrap(~ source)
```

### 2023-06-16 data-raw/03-Network-Attributes-by-Walkshed.Rmd
Recreated routing and walksheds after cleaning the zoning system and adding validation points

---
title: "Analysis of Network Attributes"
author: "Antonio Paez"
date: "`r Sys.Date()`"
output: html_notebook
---

@@

```{r}
load(file = "hamilton_net.rda")
load(file = "urban_hammer_da.rda")
load(file = "walksheds.rda")
```

@@

# Initialize data frame
walksheds_net_attributes <- data.frame(GeoUID = walksheds$GeoUID,
                                       n_nodes = numeric(889), 
                                       transitivity = numeric(889),
                                       motifs = numeric(889),
                                       n_edges = numeric(889),
                                       diameter = numeric(889), 
                                       radius = numeric(889),
                                       girth = numeric(889), 
                                       global_efficiency = numeric(889),
                                       edge_density = numeric(889),
                                       edge_connectivity = numeric(889),
                                       mean_distance = numeric(889),
                                       min_cut = numeric(889))

for(i in 1:nrow(walksheds)){
  wsnet <- st_intersection(hamilton_edges, 
                           walksheds[i,]) |> 
    st_cast(to = "LINESTRING")
  wsnet <- as_sfnetwork(wsnet)
  E(wsnet)$weight <- E(wsnet)$length
  walksheds_net_attributes$n_nodes[i] <- gorder(wsnet)
  walksheds_net_attributes$transitivity[i] <- transitivity(wsnet)
  walksheds_net_attributes$motifs[i] <- count_motifs(wsnet)
  walksheds_net_attributes$n_edges[i] <- gsize(wsnet)
  walksheds_net_attributes$diameter[i] <- diameter(wsnet)
  walksheds_net_attributes$radius[i] <- radius(wsnet)
  walksheds_net_attributes$girth[i] <- girth(wsnet)$girth
  walksheds_net_attributes$global_efficiency[i] <- global_efficiency(wsnet)
  walksheds_net_attributes$edge_density[i] <- edge_density(wsnet)
  walksheds_net_attributes$edge_connectivity[i] <- edge_connectivity(wsnet)
  walksheds_net_attributes$mean_distance[i] <- mean_distance(wsnet)
  walksheds_net_attributes$min_cut[i] <- min_cut(wsnet)
}

@@

Join the type of urban fabric:
```{r}
walksheds_net_attributes <- walksheds_net_attributes |>
  mutate(Type = walksheds$Type) |>
  select(GeoUID, Type, n_nodes:min_cut)
```

Save the data object:
```{r}
save(walksheds_net_attributes, file = "walksheds_net_attributes.rda", compress = "xz")
```

```{r}
walksheds_net_attributes |>
  group_by(Type) |>
  skim()
```

@@

Motifs (calculated for size 3): It indicates the presence of particular subgraphs that repeat themselves. In other words, a graph with a large number of motifs will tend to have few unique elements (some elements happen again, again, and again). A graph with many unique elements will have few motifs (repetitive patterns).

>>>>

---
title: "Network Attributes by Walkshed"
author: "Antonio Paez"
date: "`r Sys.Date()`"
output: html_notebook
---

@@

```{r}
load(file = "hamilton_net.rda")
load(file = "urban_hammer_da.rda")
load(file = "walksheds_da.rda")
load(file = "walksheds_validation.rda")
```

@@

# Initialize data frame
walksheds_da_net_vars <- data.frame(GeoUID = walksheds_da$GeoUID,
                                       n_nodes = numeric(nrow(walksheds_da)), 
                                       transitivity = numeric(nrow(walksheds_da)),
                                       motifs_3 = numeric(nrow(walksheds_da)),
                                       motifs_4 = numeric(nrow(walksheds_da)),
                                       n_edges = numeric(nrow(walksheds_da)),
                                       diameter = numeric(nrow(walksheds_da)), 
                                       radius = numeric(nrow(walksheds_da)),
                                       girth = numeric(nrow(walksheds_da)), 
                                       global_efficiency = numeric(nrow(walksheds_da)),
                                       edge_density = numeric(nrow(walksheds_da)),
                                       edge_connectivity = numeric(nrow(walksheds_da)),
                                       mean_distance = numeric(nrow(walksheds_da)),
                                       min_cut = numeric(nrow(walksheds_da)))

for(i in 1:nrow(walksheds_da)){
  wsnet <- st_intersection(hamilton_edges, 
                           walksheds_da[i,]) |> 
    st_cast(to = "LINESTRING")
  wsnet <- as_sfnetwork(wsnet)
  E(wsnet)$weight <- E(wsnet)$length
  walksheds_da_net_vars$n_nodes[i] <- gorder(wsnet)
  walksheds_da_net_vars$transitivity[i] <- transitivity(wsnet)
  walksheds_da_net_vars$motifs_3[i] <- count_motifs(wsnet, size = 3)
  walksheds_da_net_vars$motifs_4[i] <- count_motifs(wsnet, size = 4)
  walksheds_da_net_vars$n_edges[i] <- gsize(wsnet)
  walksheds_da_net_vars$diameter[i] <- diameter(wsnet)
  walksheds_da_net_vars$radius[i] <- radius(wsnet)
  walksheds_da_net_vars$girth[i] <- girth(wsnet)$girth
  walksheds_da_net_vars$global_efficiency[i] <- global_efficiency(wsnet)
  walksheds_da_net_vars$edge_density[i] <- edge_density(wsnet)
  walksheds_da_net_vars$edge_connectivity[i] <- edge_connectivity(wsnet)
  walksheds_da_net_vars$mean_distance[i] <- mean_distance(wsnet)
  walksheds_da_net_vars$min_cut[i] <- min_cut(wsnet)
}

@@

Join the type of urban fabric:
```{r}
walksheds_da_net_vars <- walksheds_da_net_vars |>
  mutate(Type = walksheds_da$Type) |>
  select(GeoUID, Type, n_nodes:min_cut)
```

Save the data object:
```{r}
save(walksheds_da_net_vars, file = "walksheds_da_net_vars.rda", compress = "xz")
```

Calculate network attributes by walkshed for the validation set:
```{r warning=FALSE}
# Time algorithm
start.time <- Sys.time()

# Initialize data frame
walksheds_validation_net_vars <- data.frame(GeoUID = walksheds_validation$GeoUID,
                                       n_nodes = numeric(nrow(walksheds_validation)), 
                                       transitivity = numeric(nrow(walksheds_validation)),
                                       motifs_3 = numeric(nrow(walksheds_validation)),
                                       motifs_4 = numeric(nrow(walksheds_validation)),
                                       n_edges = numeric(nrow(walksheds_validation)),
                                       diameter = numeric(nrow(walksheds_validation)), 
                                       radius = numeric(nrow(walksheds_validation)),
                                       girth = numeric(nrow(walksheds_validation)), 
                                       global_efficiency = numeric(nrow(walksheds_validation)),
                                       edge_density = numeric(nrow(walksheds_validation)),
                                       edge_connectivity = numeric(nrow(walksheds_validation)),
                                       mean_distance = numeric(nrow(walksheds_validation)),
                                       min_cut = numeric(nrow(walksheds_validation)))

for(i in 1:nrow(walksheds_validation)){
  wsnet <- st_intersection(hamilton_edges, 
                           walksheds_validation[i,]) |> 
    st_cast(to = "LINESTRING")
  wsnet <- as_sfnetwork(wsnet)
  E(wsnet)$weight <- E(wsnet)$length
  walksheds_validation_net_vars$n_nodes[i] <- gorder(wsnet)
  walksheds_validation_net_vars$transitivity[i] <- transitivity(wsnet)
  walksheds_validation_net_vars$motifs_3[i] <- count_motifs(wsnet, size = 3)
  walksheds_validation_net_vars$motifs_4[i] <- count_motifs(wsnet, size = 4)
  walksheds_validation_net_vars$n_edges[i] <- gsize(wsnet)
  walksheds_validation_net_vars$diameter[i] <- diameter(wsnet)
  walksheds_validation_net_vars$radius[i] <- radius(wsnet)
  walksheds_validation_net_vars$girth[i] <- girth(wsnet)$girth
  walksheds_validation_net_vars$global_efficiency[i] <- global_efficiency(wsnet)
  walksheds_validation_net_vars$edge_density[i] <- edge_density(wsnet)
  walksheds_validation_net_vars$edge_connectivity[i] <- edge_connectivity(wsnet)
  walksheds_validation_net_vars$mean_distance[i] <- mean_distance(wsnet)
  walksheds_validation_net_vars$min_cut[i] <- min_cut(wsnet)
}

Join the type of urban fabric:
```{r}
walksheds_validation_net_vars <- walksheds_validation_net_vars |>
  mutate(Type = walksheds_validation$Type) |>
  select(GeoUID, Type, n_nodes:min_cut)
```

Save the data object:
```{r}
save(walksheds_validation_net_vars, file = "walksheds_validation_net_vars.rda", compress = "xz")
```

```{r}
walksheds_da_net_vars |>
  group_by(Type) |>
  skim()
```

```{r}
walksheds_validation_net_vars |>
  group_by(Type) |>
  skim()
```

@@

Motifs (calculated for size 3 and 4): It indicates the presence of particular subgraphs that repeat themselves. In other words, a graph with a large number of motifs will tend to have few unique elements (some elements happen again, again, and again). A graph with many unique elements will have few motifs (repetitive patterns).
